Conference Paper Title\\

### 2023-06-14 LARS_paper/paper.tex
Fix references

The joints' controllers is the Joint Trajectory Controller, a controller of ROS which executes joint-space trajectories on a group of joints. According to \cite{joint-trajectory}, trajectories are specified as a set of waypoints to be reached at specific time instants, which the controller attempts to execute as well as the mechanism allows. In this work, the waypoints consist of positions and are reached using PID controllers loop-closed.

@@

\begin{thebibliography}{00}
  \bibitem{X.134} X. Zhang, L. Lang, J. Wang, and H. Ma, ‘The quadruped robot locomotion based on force control’, Proceedings of the 2015 27th Chinese Control and Decision Conference, CCDC 2015, pp. 5440–5445, 2015.
  \bibitem{ROS2Humble} S. Macenski, T. Foote, B. Gerkey, C. Lalancette, and W. Woodall, ‘Robot Operating System 2: Design, architecture, and uses in the wild’, Science Robotics, vol. 7, no. 66, p. eabm6074, 2022.
  \bibitem{Shi2021} Y. Shi, S. Li, M. Guo, Y. Yang, D. Xia, and X. Luo, ‘Structural design, simulation and experiment of quadruped robot’, Applied Sciences (Switzerland), vol. 11, 2021.
  \bibitem{leotti2005comparaccao} V. B. Leotti, A. R. Birck, and J. Riboldi, ‘Comparação dos Testes de Aderência à Normalidade Kolmogorov-smirnov, Anderson-Darling, Cramer--Von Mises e Shapiro-Wilk por Simulação’, Anais do 11\textordmasculine Simpósio de Estatística Aplicada à Experimentação Agronômica, 2005.
  \bibitem{cano2012six} E. L. Cano, J. M. Moguerza, and A. Redchuk, Six sigma with R: statistical engineering for process improvement, vol. 36. Springer Science \& Business Media, 2012.
  \bibitem{CaramelRepo} B. S. de Alencar, F. M. S. M. Barreto, and L. L. Souza (2022), ‘Caramel’, [Source Code]. https://github.com/Brazilian-Institute-of-Robotics/bir-black-mouth.
  \bibitem{Kitano2016} S. Kitano, S. Hirose, A. Horigome, and G. Endo, ‘TITAN-XIII: sprawling-type quadruped robot with ability of fast and energy-efficient walking’, ROBOMECH Journal, vol. 3, pp. 1–16, 2016.
  \bibitem{Zhong2019} Y. Zhong, R. Wang, H. Feng, and Y. Chen, ‘Analysis and research of quadruped robot’s legs: A comprehensive review’, International Journal of Advanced Robotic Systems, vol. 16, 3 2019.
  \bibitem{de2006quadrupedal} P. G. De Santos, E. Garcia, and J. Estremera, Quadrupedal locomotion: an introduction to the control of four-legged robots, vol. 1. Springer, 2006.
  \bibitem{StanfordQuadruped} N. Kau, A. Z. Schultz, and M. Bowers, Stanford Quadruped (2021), [Source Code]. https://github.com/stanfordroboticsclub/StanfordQuadruped.

>>>>

The joints' controllers is the Joint Trajectory Controller, a controller of ROS which executes joint-space trajectories on a group of joints. According to \cite{JointTrajectory}, trajectories are specified as a set of waypoints to be reached at specific time instants, which the controller attempts to execute as well as the mechanism allows. In this work, the waypoints consist of positions and are reached using PID controllers loop-closed.

@@

\begin{thebibliography}{00}
  \bibitem{X.134} X. Zhang, L. Lang, J. Wang, and H. Ma, ‘The quadruped robot locomotion based on force control’, Proceedings of the 2015 27th Chinese Control and Decision Conference, CCDC 2015, pp. 5440–5445, 2015.
  \bibitem{ROS2Humble} S. Macenski, T. Foote, B. Gerkey, C. Lalancette, and W. Woodall, ‘Robot Operating System 2: Design, architecture, and uses in the wild’, Science Robotics, vol. 7, no. 66, p. eabm6074, 2022.
  \bibitem{Shi2021} Y. Shi, S. Li, M. Guo, Y. Yang, D. Xia, and X. Luo, ‘Structural design, simulation and experiment of quadruped robot’, Applied Sciences (Switzerland), vol. 11, 2021.
  \bibitem{leotti2005comparaccao} V. B. Leotti, A. R. Birck, and J. Riboldi, ‘Comparação dos Testes de Aderência à Normalidade Kolmogorov-smirnov, Anderson-Darling, Cramer--Von Mises e Shapiro-Wilk por Simulação’, Anais do 11\textordmasculine Simpósio de Estatística Aplicada à Experimentação Agronômica, 2005.
  \bibitem{cano2012six} E. L. Cano, J. M. Moguerza, and A. Redchuk, Six sigma with R: statistical engineering for process improvement, vol. 36. Springer Science \& Business Media, 2012.
  \bibitem{CaramelRepo} B. S. de Alencar, F. M. S. M. Barreto, and L. L. Souza (2022), ‘Caramel’. Github.com. https://github.com/Brazilian-Institute-of-Robotics/bir-black-mouth. (Accessed Jun. 13, 2023).
  \bibitem{Kitano2016} S. Kitano, S. Hirose, A. Horigome, and G. Endo, ‘TITAN-XIII: sprawling-type quadruped robot with ability of fast and energy-efficient walking’, ROBOMECH Journal, vol. 3, pp. 1–16, 2016.
  \bibitem{Zhong2019} Y. Zhong, R. Wang, H. Feng, and Y. Chen, ‘Analysis and research of quadruped robot’s legs: A comprehensive review’, International Journal of Advanced Robotic Systems, vol. 16, 3 2019.
  \bibitem{de2006quadrupedal} P. G. De Santos, E. Garcia, and J. Estremera, ‘Quadrupedal locomotion: an introduction to the control of four-legged robots’, vol. 1. Springer, 2006.
  \bibitem{StanfordQuadruped} N. Kau, A. Z. Schultz, and M. Bowers, ‘Stanford Quadruped’. Github.com. https://github.com/stanfordroboticsclub/StanfordQuadruped. (Accessed Jun. 13, 2023).
  \bibitem{JointTrajectory} ros2\_control Development Team. ‘Joint Trajectory Controller’. Control.ros.org. https://control.ros.org/foxy/doc/ros2\_controllers/joint\_trajectory\_contro
  ller/doc/userdoc.html. (Accessed Jun. 13, 2023).
